My title: still thinking

### 2024-04-14 paper/paper.qmd
Added datasheet

>>>>

Keep member distribution?

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-member_distribution
#| fig-cap: Distribution of Members of Top 10000 Anime

mean_members <- mean(clean_anime$num_list_users)

clean_anime %>%
  ggplot(aes(x = num_list_users)) +
  geom_histogram(binwidth=50000, color="darkblue", fill="lightblue") +
  theme_minimal() +
  geom_vline(aes(xintercept=mean_members), linetype="dashed", size=1) +
  annotate("text", x = mean_members + 0.1, y = 550, label = paste("Mean Members", round(mean_members, 2)), 
           hjust = 0, vjust = -1) +
  labs(x = "Members", y = "count")
```
